### 2017-02-04 2017mergingmerges/section/XX-Fusion.tex
ok

The core fusion algorithm works by constructing a static schedule for a pair of processes, which can be repeated over the whole network until only one process remains.
The static schedule mirrors the dynamic evaluation by statically performing injection and shaking on the two processes.
Figure~\ref{fig:Fusion:Types} shows the type definitions for fusion.
Because the fused process is \emph{statically} evaluating both processes, we use its labels to encode static information about the dynamic state of the original processes.
The fused label contains the pair of both original labels, as well as the static part of the $\InputState$ for each input channel.
If the static $\InputState_S$ is $@pending@_S$, there is a value waiting to be pulled, but rather than knowing its actual value as in the dynamic evaluation, we know its value is stored in the $@chan@$ variable for that channel.

>>>>

The core fusion algorithm works by constructing a static schedule for a pair of processes, which is repeated over the whole network until only one process remains.
The static schedule mirrors the dynamic evaluation by statically performing injection and shaking on the two processes.
Figure~\ref{fig:Fusion:Types} shows the type definitions for fusion.
Because the fused process is \emph{statically} evaluating both processes, we use its labels to encode static information about the dynamic state of the original processes.
The fused label contains the pair of both original labels, as well as the static part of the $\InputState$ for each input channel.
If the static $\InputState_S$ is $@pending@_S$, there is a value waiting to be pulled, but rather than knowing its actual value as in the dynamic evaluation, we know its value is stored in the $@chan@$ variable for that channel.

### 2017-02-04 2017mergingmerges/section/XX-Processes.tex
ok

The grammar for processes is shown in figure~\ref{fig:Process:Def}.
Channels, labels and variables are specified by some external, globally unique set of names.
We assume that values and expressions are specified externally to the core calculus.
The actual details of the external computation are not important, except that there should be an evaluation form taking a heap and an expression and producing a value, as well as some way to destruct booleans.

@@

The heap is used for evaluation - it is used when evaluating the external value calculus.
Each process has its own private heap, meaning that the only communication between processes occurs by streams.

@@

Pulling from a stream is blocking, and as usual with Kahn processes~\cite{kahn1976coroutines}, there is no way to tell whether a stream currently has a value.
Pull takes as arguments the channel to read from, the variable to put the read value in, and the next label state to jump to after a successful pull.

After values have been pulled, they must be disposed of with @drop@.
This has no real evaluation semantics other than for coordination between processes.

>>>>

The grammar for processes is shown in figure~\ref{fig:Process:Def}.
Channels, labels and variables are specified by some external, globally unique set of names.
For values and expressions we use a simple untyped lambda calculus with a few primitives chosen to facilitate the examples.

@@

The heap is used for evaluation of expressions.
Each process has its own private heap, meaning that the only communication between processes occurs by streams.

@@

As usual with Kahn processes~\cite{kahn1976coroutines}, pulling from a channel is blocking.
Unlike normal Kahn processes however, pushing to a channel can also block: each consumer has a single-element buffer and pushing only succeeds when all buffers are empty.
After values have been pulled, they must be disposed of with @drop@: this empties the value from the buffer and allows the producer process to push to that stream.
